Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-07 paper/paper.tex
pass on technique

@@

The goal of the first step is to extract options from the positive
traffic. For that, \tname{} parses the protocol message, looking for
fields in the message associated with options (see
Section~\ref{sec:rules-and-packets}).
Unfortunately, inferring options at the field granularity
level is insufficient to capture \CodeIn{content} options (see
Section~\ref{sec:example-suricata-rules}), which refer to parts of the
payload of the message and cannot be directly extracted directly from
the fields. Handling this case is critically important as most rules
contain \CodeIn{content}
options. Figure~\ref{fig:distribution-contents} shows the histogram of
number of these options per rule (up to 10) obtained from a public
ruleset~\cite{emerging-threats-open} containing 27.8K Suricata
rules. Rules without \CodeIn{content} options is an exception and half
of the rules contain at least two \CodeIn{content} options.  To find
the values associated with these options, \tname{} splits the payload
of the malicious message in tokens using natural language delimiters,
such as $\backslash$t, $\backslash$n, $\backslash$r, and spaces. The
rationale for this decision is that we observed, by inspecting
existing rules, that \CodeIn{content} options typically refer to
sequence of characters in the payload of messages separated by these
delimiters. This tokenization step can generate dozens of options. For
the example from Section~\ref{sec:content-example}, \tname{} produces
a total of \Fix{xx} content options.

>>>>

The goal of the first step is to extract options from the positive
traffic. For that, \tname{} parses the protocol message, looking for
fields in the message associated with options (see
Section~\ref{sec:rules-and-packets}).  Unfortunately, inferring
options at the field granularity level is insufficient to capture
\CodeIn{content} options (see
Section~\ref{sec:example-suricata-rules}), which refer to parts of the
payload of the message and cannot be extracted directly from the
fields. Handling this case is critically important as \Fix{xx}\% of the
rules contain \CodeIn{content} options as the one from
Section~\ref{sec:content-example}.

@@

Figure~\ref{fig:distribution-contents} shows the histogram of the
number of these options per rule (up to 10) obtained from a public
ruleset~\cite{emerging-threats-open} containing 27.8K Suricata
rules. Rules without \CodeIn{content} options is an exception and half
of the rules contain at least two \CodeIn{content} options.  To find
the values associated with these options, \tname{} splits the payload
of the malicious message in tokens using natural language delimiters,
such as $\backslash$t, $\backslash$n, $\backslash$r, and spaces. We
observed, by inspecting existing rules, that \CodeIn{content} options
typically refer to sequence of characters in the payload of messages
separated by these delimiters. This tokenization step can generate
dozens of options. For the example from
Section~\ref{sec:content-example}, \tname{} produces a total of
\Fix{xx} content options.

\Mar{pessoal, isto explica como inferimos opcoes de content, mas nao
  explica como inferimos as outras opcoes. Em particular, as opcoes
  dos primeiros dois exemplos da Secao 3.}

\Mar{-------------------------------- estou aqui}
